
\chapter*{Acknowledgements}

My deepest gratitude goes to Prof.\,Dr.\,Dr. Wolfgang Rhode for giving me the opportunity to 
work in the field of astroparticle physics and for supervising this thesis.
I also thank my second supervisor Prof.\,Dr. Kevin Kröninger for his interest in my research topic.

This work would never have been possible without the continuous support of my fellow colleagues and friends in the 
astroparticle physics group at Dortmund. It truly is a thoroughly pleasant environment to work in. 
Special thanks go out to Jens Buss, for essentially recruiting me and being the moral compass of the department, 
Lena Linhoff, for enduring my prolonged presence in her office, and Alexander Sandrock, for guiding me through horrible integral transforms.
In particular, I'd like to thank my office mate and physics partner-in-crime Maximilian Nöthe. Thanks for teaching 
me innumerable things about \python, \LaTeX and programming in general, not to mention my appreciation for active-noise-canceling technology. 
I'd like to give special thanks to everyone who took on the daunting task of 
proofreading this document: Lena Linhoff, Maximilian Nöthe, and Linda Richerd. 

Finally I can't help but acknowledge the Sonderforschungsbereich 876 for its funding 
and for giving me the opportunity to travel and meet all the terrific people that make up the CTA consortium.
A special thanks to the SFB for allowing me to work at the CEA institute in Paris during the early stages of my graduate studies.
Thanks to Thierry Stolarczyk for hosting me at CEA, Karl Kosack 
for many helpful discussions and supporting open science for CTA, and the entire group at CEA. 

I owe additional gratitude to all my friends and family who did not get to see me much during the last few months. 
In particular I'd like to thank Hannah for putting up with my late-night antics and unusual dinner schedule.
